Moral Foundations of U.S. Political News Organizations

### 2019-04-01 pilot_manuscript.Rmd
small changes to the draft

Political articles were collected from the websites of four notable U.S. news sources, a process known as web scraping. The sources were *The New York Times*, *National Public Radio (NPR)*, *Fox News*, and *Breitbart*. They were selected for their widespread recognition and the fact politcial partisans have strong preferences for some sources over others. The researchers determined the political lean of each source by referencing @Mitchell2014's article demonstrating the self-reported idealogical consistency represented by the consumers of several news sources. In general, *The New York Times* and *NPR* are preferred by consumers reporting a liberal bias or lean. In contrast, Fox News and Breitbart are believed to have a conservative bias or lean. @Mitchell2014's article presented political ideology as a scale ranging from "consistently liberal" to "consistently conservative." In between these extremes lie more moderate positions, including "mostly liberal," "mixed," and "mostly conservative." Owing to the lower number of sources analyzed herein, the researchers elected to categorize the sources as either "liberal" and "conservative" in order to form a basis for comparison.

@@

##U.S. Government Shutdown of 2018-2019

The U.S. Federal Government partially shut down on December 22, 2018. The government reopened on January 25, 2019 upon the passage of an appropriations bill by both houses of Congress [@Axelrod2019]. The shutdown stemmed from a disagreement between President Donald Trump and Congress over funding for the president's proposed U.S.-Mexico border waLL. President Trump demanded $5.7 billion dollars in the new budget to be appropriated for the wall, which Congress did not provide in its budget [@Peoples2019]. Owing to the lack of funding, the government began a partial shutdown, causing "around 800,000" federal employees to be either furloughed or compelled to work without pay [@Axelrod2019].

@@

tiff(filename = "exp2_graph_kav.tiff", res = 300, width = 4, 
     height = 3, units = 'in', compression = "lzw")
plot(graph_data_kav)
dev.off()

@@

tiff(filename = "exp2_graph_gs.tiff", res = 300, width = 4, 
     height = 3, units = 'in', compression = "lzw")
plot(graph_data_gs)
dev.off()

```
# Discussion

>>>>

Political articles were collected from the websites of four notable U.S. news sources, a process known as web scraping. The sources were *The New York Times*, *National Public Radio (NPR)*, *Fox News*, and *Breitbart*. They were selected for their widespread recognition and the fact politcial partisans have strong preferences for some sources over others. The researchers determined the political lean of each source by referencing @Mitchell2014's article demonstrating the self-reported idealogical consistency represented by the consumers of several news sources. In general, *The New York Times* and *NPR* are preferred by consumers reporting a liberal bias or lean. In contrast, *Fox News* and *Breitbart* are believed to have a conservative bias or lean. @Mitchell2014's article presented political ideology as a scale ranging from "consistently liberal" to "consistently conservative." In between these extremes lie more moderate positions, including "mostly liberal," "mixed," and "mostly conservative." Owing to the lower number of sources analyzed herein, the researchers elected to categorize the sources as either "liberal" and "conservative" in order to form a basis for comparison.

@@

## U.S. Government Shutdown of 2018-2019

The U.S. Federal Government partially shut down on December 22, 2018. The government reopened on January 25, 2019 upon the passage of an appropriations bill by both houses of Congress [@Axelrod2019]. The shutdown stemmed from a disagreement between President Donald Trump and Congress over funding for the president's proposed U.S.-Mexico border wall. President Trump demanded $5.7 billion dollars in the new budget to be appropriated for the wall, which Congress did not provide in its budget [@Peoples2019]. Owing to the lack of funding, the government began a partial shutdown, causing "around 800,000" federal employees to be either furloughed or compelled to work without pay [@Axelrod2019].

@@

tiff(filename = "exp2_graph_kav.tiff", res = 300, width = 4, 
     height = 3, units = 'in', compression = "lzw")
plot(graph_data_kav)
dev.off()
```

@@

tiff(filename = "exp2_graph_gs.tiff", res = 300, width = 4, 
     height = 3, units = 'in', compression = "lzw")
plot(graph_data_gs)
dev.off()
=
```
